### 2021-04-02 Chapter-3/Chapter-3.tex
update

An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable.

\subsection{Secret-dependent Data Accesses}
Similar to secret-dependent control-flow transfers, a data access operation is
secret-dependent if different input sensitive keys ($K$) can lead to different
memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits
of the address are irrelevant in side-channels.

We consider a data access is secret-dependent if:
$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$

@@

With the above definitions, we can model an attacker's observation by a series of math formulas. For example, in Figure~\ref{fig:side-channel}, if an attacker observes
the code executes the branch 1, we have $c_5: k_1 + k_2 < 4$ to describe an
attacker's knowledge and $K^{o5} = \{k_1,\, k_2\,|\, (k_1 + k_2) < 4\}$. If an
attacker observes the code executes the branch 2, we have $c_8: k_1 - k_2 > 0$
and $K^{o8} = \{k_1,\, k_2\,|\, (k_1 - k_2) > 0\}$.
\section{Scalability}
\subsection{Trace-oriented Symbolic Execution}
While symbolic execution can capture fine-grained semantics of programs, it
is also notorious for its unbearable performance cost. Previous trace-oriented
symbolic execution based
works~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} all have large
performance bottlenecks. As a result, those approaches either only apply to
small-size programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or apply some
domain knowledge to simplify the analysis. 
%Those tools interpret each
%instruction and update memory cells and registers with formulas that
%captured the semantics of the execution and search different input values that
%can lead to different execution behaviors using constraint solver. 
We implement the approach presented in \S\ref{sec:trace-qif} and model the side-channels as formulas. While the tool can finish analyzing some simple cases like AES, it can
not handle complicated cases like RSA.
We observe that finding side-channels using symbolic execution is different from
traditional general symbolic execution and can be optimized to be as efficient
as other methods with approaches below.

>>>>

An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above
inequation. For example, in the example from Figure~\ref{fig:chapter3:cf}, if $m = 0$,
the code will always execute the branch 2. However, the function \textsf{example1} still
has a secret-dependent control-flow for some $m$, so we think the code has
some side-channel leakages.

\subsection{Secret-dependent Data Accesses}
Similar to secret-dependent control-flow transfers, a data access operation is
secret-dependent if different input sensitive keys ($K$) cause access to different
memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits
of the address are generally unimportant in side-channels.

A data access is secret-dependent if:

$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$

@@

\section{Scalability}
\subsection{Trace-oriented Symbolic Execution}
While symbolic execution can capture fine-grained semantics of programs, it
is also notorious for its unbearable performance cost. Previous trace-oriented
symbolic execution based
works~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} all have large
performance bottlenecks. As a result, those approaches either only apply to
small-size programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or apply some
domain knowledge to simplify the analysis. 
%Those tools interpret each
%instruction and update memory cells and registers with formulas that
%captured the semantics of the execution and search different input values that
%can lead to different execution behaviors using constraint solver. 
We implement the approach presented in \S\ref{sec:trace-qif} and model the side-channels as formulas. While the tool can finish analyzing some simple cases like AES, it can
not handle complicated cases like RSA.
We observe that finding side-channels using symbolic execution is different from
traditional general symbolic execution and can be optimized to be as efficient
as other methods with approaches below.
